### 2017-08-29 etc/2017-08-28_VPD_uWUE_notes/explicit.tex
redoing calc derivative to be correct
put all units into Pa, better this way but could be some lingering errors
NOTE DELETING OLD PLOTTING CODE THAT COULD BE USEFUL, also found order of mangitude error in new model but still not 1:1

where from Medlyn we have:
\begin{equation}
  g_s = \text{LAI } 1.6 \left(1 + \frac{g_1}{\sqrt{D_{s}}}\right) \frac{A}{c_s}
\end{equation}

@@

Then we can show that if we multiply $g_s$ by $\frac{ uWUE \; ET}{A \sqrt{D_s}}$ (which is equivalent to 1 with unit conversion above), we can rearrange Penman Moneith to get:

\begin{equation}
  \lambda E = \frac{\Delta R + g_a \left( \rho_a c_p D_{s} - \frac{\gamma c_s \sqrt{D_s}}{\text{LAI }1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})} \right) }{ \Delta + \gamma}
\end{equation}

If we want to solve for LAI as a function of all other knowns, we have:
\begin{equation}
LAI  = \frac{g_a \gamma c_s \sqrt{D_s}}{ \left(\text{ ET } ( \Delta + \gamma) - \Delta R - g_a \rho_a c_p D_{s}\right) 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})}
\end{equation}

@@

\begin{equation}
\frac{\partial \;  \lambda E}{\partial \; D_s} = \frac{g_a}{\Delta + \gamma}   \left( \rho_a c_p - \frac{\gamma c_s }{\text{LAI }1.6 \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D_s}}{2 (g_1 + \sqrt{D_s})^2}\right) \right)
\end{equation}

>>>>

where from Medlyn we have:
\begin{equation}
  g_s = \text{LAI } \frac{R T}{P} 1.6 \left(1 + \frac{g_1}{\sqrt{D_{s}}}\right) \frac{A}{c_s}
\end{equation}

@@

Then we can show that if we multiply $g_s$ by $\frac{ uWUE \; ET}{A \sqrt{D_s} L_v}$ (which is equivalent to 1 with unit conversion above), we can rearrange Penman Moneith to get:

\begin{equation}
  \lambda E = \frac{\Delta R + g_a \left( \rho_a c_p D_{s} - \frac{\gamma c_s \sqrt{D_s} L_v P }{\text{LAI } R \; T \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})} \right) }{ \Delta + \gamma}
\end{equation}

If we want to solve for LAI as a function of all other knowns, we have:
\begin{equation}
LAI  = \frac{g_a \gamma c_s \sqrt{D_s} L_v P }{ \left(\text{ ET } ( \Delta + \gamma) - \Delta R - g_a \rho_a c_p D_{s}\right) 1.6 \; R\; T\; \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})}
\end{equation}

@@

\begin{equation}
\frac{\partial \;  \lambda E}{\partial \; D_s} = \frac{g_a}{\Delta + \gamma}   \left( \rho_a c_p - \frac{\gamma c_s L_v  P }{\text{LAI }1.6 \; R\; T \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D_s}}{2 (g_1 + \sqrt{D_s})^2}\right) \right)
\end{equation}
